\documentclass[a3paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[british]{babel}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage[margin=1cm]{geometry}
\usepackage{titling}
\usepackage[dvipsnames,svgnames,x11names]{xcolor}
\usepackage[hyphens]{url}
\usepackage{xparse}

\title{Conferences in Security and Privacy by Deadline}

\begin{document}
\pagestyle{empty}
\begin{center}
  \LARGE\bfseries\thetitle{}
\end{center}
\DeclareDocumentCommand{\tierone}{o}{%
  \IfNoValueTF{#1}{\color{red}}{\textcolor{red}{#1}}%
}
\DeclareDocumentCommand{\tiertwo}{o}{%
  \IfNoValueTF{#1}%
  {\color{yellow}}{\textcolor{yellow}{#1}}%
}
\DeclareDocumentCommand{\tierthree}{o}{%
  \IfNoValueTF{#1}{\color{green}}{\textcolor{green}{#1}}%
}
\DeclareDocumentCommand{\tierfour}{o}{%
  \IfNoValueTF{#1}%
  {\color{cyan}}{\textcolor{cyan}{#1}}%
}
\DeclareDocumentCommand{\tierfive}{o}{%
  \IfNoValueTF{#1}{\color{blue}}{\textcolor{blue}{#1}}
}


\begin{longtable}{p{2cm}p{7cm}llp{3cm}p{9cm}}
  \textbf{Acronym}\footnote{%
    \tierone{Tier 1}, \tiertwo{Tier 2}, \tierthree{Tier 3}, \tierfour{Tier 4}, 
    \tierfive{Tier 5}, Unknown ranking.
    Sources: 
    \url{http://icsd.i2r.a-star.edu.sg/staff/jianying/conference-ranking.html},
    \url{http://faculty.cs.tamu.edu/guofei/sec_conf_stat.htm},
    \url{https://personal.cis.strath.ac.uk/changyu.dong/ranking.html},
    \url{http://academic.research.microsoft.com/RankList?entitytype=3&topdomainid=2&subdomainid=2&last=0&orderby=1},
    \url{https://scholar.google.com/citations?view_op=top_venues&vq=eng_computersecuritycryptography},
    \url{http://lipn.univ-paris13.fr/~bennani/CSRank.html},
    \url{http://www.wi2.uni-erlangen.de/_fileuploads/research/generic/ranking/index.html}.
  } & \textbf{Title}
  & \textbf{Submission} & \textbf{Event} & \textbf{LaTeX format}
  & \textbf{Comment} \\
  \toprule

  \tierfour{IFIP SEC}
  & IFIP International Information Security and Privacy Conference
  & January & June & llncs, biblatex-lncs
  & 14 pages total.
  \\

  \midrule

  \tierfour{ACNS}
  & International Conference on Applied Cryptography and Network Security
  & January & June & llncs, biblatex-lncs
  & 18 pages incl.~references, appendices may be added without limit.
  \\

  \midrule

  \tierone{SIGCOMM}
  & ACM Special Interest Group on Data Communication
  & January & August & acm-alternate
  & 12 pages excl.~references.
  \tierone[Networking].
  \\

  \midrule

  \tierone{PODC}
  & Symposium on Principles of Distributed Computing
  & February & July & acm
  & Submission: regular paper 10 pages, brief announcement 3 pages.
  \\

  \midrule

  \tierone{USENIX SEC}
  & USENIX Security Symposium
  & February & August & usenix
  & Submissions: 13 pages, excl.~bibliography and appendices.
  Accepted papers: fit in 16 pages, incl.~bibliography and appendices.
  \\

  \midrule

  \tierone{CRYPTO}
  & International Cryptology Conference
  & February & August & llncs, biblatex-lncs
  & Submission: 18 pages excl.~references and appendices.
  Accepted paper: 18 pages total.
  \\

  \midrule

  \tiertwo{PETS}
  & Privacy Enhancing Technologies Symposium
  & February & July & acmproc
  & 10 pages excl.~bibliography and appendices, 15 pages total.
  \tierone[PETs], \tierone[DOSN].
  \\

  \midrule

  \tierthree{CSF}
  & Computer Security Foundations Symposium
  & February & July & ieee
  & 12 pages excl.~bibliography and appendices.
  \\

  \midrule

  \tierfour{SACMAT}
  & ACM Symposium on Access Control Models and Technologies
  & February & June & acmproc
  & 10 US letter pages excl.~appendices, 12 pages total.
  \\

  \midrule

  \tierfour{DBSec}
  & Annual IFIP WG 11.3 Working Conference on Data and Applications Security 
  and Privacy
  & February & July & llncs, biblatex-lncs
  & 16 pages total.
  \\

  \midrule

  \tierfour{SOUPS}
  & Symposium On Usable Privacy and Security
  & March & July & soups
  & 12 pages excl.~bibliography and appendices,20 pages total.
  \\

  \midrule

  PST & International Conference on Privacy, Security and Trust
  & March & July & ieee
  & Regular papers: up to 8 pages.
  Short papers: up to 4 pages.
  \\

  \midrule

  \tiertwo{PETS}
  & Privacy Enhancing Technologies Symposium
  & April & July & acmproc
  & 10 pages excl.~bibliography and appendices, 15 pages total.
  \tierone[PETs], \tierone[DOSN].
  \\

  \midrule

  \tierone{TrustCom}
  & IEEE/IFIP International Conference on Trust, Security and Privacy in 
  Computing and Communications
  & April & August & ieee
  & 8 pages total.
  \\

  \midrule

  \tierfour{ESORICS}
  & European Symposium on Research in Computer Security
  & April & September & llncs, biblatex-lncs
  & 16 pages excl.~bibliography and appendices, 20 pages total.
  Purely theoretical papers, e.g.\ in cryptography, must be explicit about the 
  relevance of the theory to the security of IT systems.
  \\

  \midrule

  \tierfour{NSPW}
  & New Security Paradigms Workshop
  & April & September & acmproc
  & Regular paper: 6--15 pages.
  Student paper: 12 pages maximum.
  \\

  \midrule

  \tierfive{SCN}
  & Security and Cryptography for Networks
  & April & September & llncs, biblatex-lncs
  & 14 pages excluding the title page, bibliography and appendices.
  \\

  \midrule

  \tiertwo{P2P}
  & International Conference on Peer-to-Peer Computing
  & April & September & ieee
  & 10 pages.
  \tierone[Decentralized Systems, P2P].
  \\

  \midrule

  \tierfive{SAC}
  & Conference on Selected Areas in Cryptography
  & May & August & llncs, biblatex-lncs
  & 12 pages excl.~bibliography and appendices, 24 pages total.
  \\

  \midrule

  \tierone{CCS}
  & ACM Conference on Computer and Communications Security
  & May & November & acmproc
  & 12 pages total.
  \\

  \midrule

  \tiertwo{COSN}
  & ACM Conference on Online Social Networks
  & May & October & acmproc
  & Very selective.
  Full papers: 12 pages incl.~references.
  Short papers: 6 pages incl.~references.
  \tierone[OSN].
  \\

  \midrule

  \tiertwo{DISC}
  & Symposium on Distributed Computing
  & May & October & LIPIcs
  & Regular paper: 15 pages incl.\ references.
    Brief announcement: 3 pages.
  \\

  \midrule

  NordSec & Nordic Conference on Secure IT Systems
  & June & October & llncs, bilatex-lncs
  & Full papers: 16 pages total incl.~references and appendices.
  Short papers: 6 pages total.
  \\

  \midrule

  \tierthree{ACSAC}
  & Annual Computer Security Applications Conference
  & June & December & acmproc
  & 10 pages total.
  \\

  \midrule

  \tierfour{IMA-CCC}
  & IMA International Conference on Cryptography and Coding
  & June & December & llncs, biblatex-lncs
  & 14 pages excl.~title and abstract, bibliography and appendices.
  \\

  \midrule

  \tierfour{SecureComm}
  & International Conference on Security and Privacy in Communication Networks
  & June & October & lnicst
  & Regular papers: up to 18 pages.
  Short papers: up to 9 pages.
  Doctoral papers: 7 pages.
  Posters: 5 pages.
  \\

  \midrule

  DPM & International Workshop on Data Privacy Management
  & June & September & llncs, biblatex-lncs
  & Privacy Information Management; Privacy-oriented Access Control Languages 
  and Models; Privacy Preserving Data Mining; \tierfive[Privacy in Social 
  Networks]; Privacy Monitoring and Auditing; Privacy Services.
  Regular papers: 16 pages incl.~references.
  Short or position papers: 8 pages incl.~references.
  \\

  \midrule

  WPES & Workshop on Privacy in the Electronic Society
  & July & October & acmproc
  & Regular paper: 10 pages excl.~appendices, 12 pages total.
  Short paper: 4 pages total.
  \\

  \midrule

  SEC-T & Technical Security
  & July & September & -
  & Always in Stockholm \\

  \midrule

  \tierone{INFOCOM}
  & IEEE International Conference on Computer Communications
  & July & April & ieee
  & Strict 9 pages total.
  IEEEtran: 10pt, conference, letterpaper.
  \tierone[Network theory], practical + theoretical bounds.
  \\

  \midrule

  \tierfive{ICISS}
  & International Conference on Information Systems Security
  & July & December & llncs, biblatex-lncs
  & 20 pages incl.~references.
  \\

  \midrule

  \tiertwo{PETS}
  & Privacy Enhancing Technologies Symposium
  & August & July & acmproc
  & 10 pages excl.~bibliography and appendices, 15 pages total.
  \tierone[PETs], \tierone[DOSN].
  \\

  \midrule

  \tiertwo{NDSS}
  & ISOC Network and Distributed System Security Symposium
  & August & February & ndss
  & SENT Workshop on Security of Emerging Networking Technologies,
  USEC Workshop on Usable Security.
  \\

  \midrule

  \tierfive{ICISC}
  & International Conference on Information Security and Cryptology
  & August & November & llncs, biblatex-lncs
  & 12 pages excl.~bibliography and appendices.
  \\

  \tiertwo{EuroS\&P}
  & IEEE European Symposium on Security and Privacy
  & August & March & IEEEtran (CompSoc Conference)
  & Anonymous submission.
  15 (US letter) pages total, incl.\ references and appendices.
  \\

  \midrule

  \tiertwo{NSDI}
  & USENIX Symposium on Networked Systems Design and Implementation
  & September & April & usenix
  & Not RoMEO green?
  12 pages excl.~references.
  \tierone[Networking].
  \\

  \midrule

  \tierone{PERCOM}
  & IEEE International Conference on Pervasive Computing and Communications
  & September & March & ieee
  & 9 pages total.
  \\

  \midrule

  \tierone{EUROCRYPT}
  & International Conference on the Theory and Applications of Cryptographic 
  Techniques
  & September & April & llncs, biblatex-lncs
  & Submission: 20 pages total.
  Accepted paper: 30 pages total.
  \\

  \midrule

  \tierfour{CODASPY}
  & Conference on Data and Application Security and Privacy
  & September & March & acmproc
  & 10 pages double-column excl.~bibliography and appendices, 12 pages total.
  \\

  \midrule

  \tierfive{SAC}
  & ACM Symposium on Applied Computing
  & September & April & acmproc
  & Trust, Reputation, Evidence and other Collaboration Know-how (TRECK).
  5000 words, 6 two-column pages.
  \\

  \midrule

  \tierfour{PKC}
  & IACR International Conference on Practice and Theory of Public-Key 
  Cryptography
  & October & March & llncs, biblatex-lncs
  & 14 pages excl.~references and bibliography.
  \\

  \midrule

  \tierfour{TCC}
  & Theory of Cryptography Conference
  & October & March & llncs, biblatex-lncs
  & No page limit, reviewers are not required to read beyond the 14th page.
  Presentation quality will be a strong factor in the acceptance decision.
  Authors are strongly encouraged to post full versions of their submissions in 
  a freely accessible online repository, such as the Cryptology ePrint archive.
  \\

  \midrule

  \tierfive{SeSoc}
  & IEEE International Workshop on Security in Social Networking
  & October & March & ieee
  & 6 pages excl.~references and appendices, 7 pages total.
  Follow PERCOM instructions.
  \tiertwo[OSN], small but relevant.
  \\

  \midrule

  \tierone{S\&P}
  & IEEE Symposium on Security and Privacy
  & November & May & ieee
  & Submission: 15 pages excl.~bibliography and appendices, 20 pages total.
  Final: 16 pages total.
  US Letter, not A4.
  \\

  \midrule

  \tiertwo{PETS}
  & Privacy Enhancing Technologies Symposium
  & November & July & acmproc
  & 10 pages excl.~bibliography and appendices, 15 pages total.
  \tierone[PETs], \tierone[DOSN].
  \\

  \midrule

  \tierthree{FSE}
  & IACR Fast Software Encryption
  & November & March & llncs, biblatex-lncs
  & Submission: 20 pages incl.~references, may add appendices.
  Final: 20 pages total.
  \\

  \midrule

  \tierthree{DSN}
  & IEEE/IFIP International Conference on Dependable Systems and Networks
  & November & June & ieee
  & Regular paper: 12 pages total.
  Practical experience report: 8 pages total.
  Demos: 8 pages total.
  \\

  \midrule

  \tierone{ICDCS}
  & International Conference on Distributed Computing Systems
  & November & June & ieee
  & Very selective, good for dist.sys.~of all kinds.
  \tierone[DOSN], \tierone[Decentralized Systems, P2P].
  \\

  \bottomrule
\end{longtable}


\end{document}
